---
title: "Data607-Assignment9"
author: "Devin Teran"
date: "3/28/2020"
output: rmdformats::readthedown
---

## Overview
The goal for this assignment is to connect and retrieve JSON data using the New York Times Movie Review API.  Once connected, we want to put this data into a dataframe and view the dataframe.  


### Necessary libraries:
```{r setup}
library(jsonlite)
library(stringr)
library(rmdformats)
library(kableExtra)
library(dplyr)
```

## Connect to API  
Using the NYT Movie Review API Key, which I signed up for on the NYT website, we will retrieve ALL movie review data and critic review data using the function **fromJSON**
```{r store-api,include=FALSE}
api_key <- 'uAV27k6TGDjnmK2RGxgd9VNCmJGb0hSU'
```

```{r get_data}
options(stringAsFactors = FALSE)
movie_review_url <- str_c('https://api.nytimes.com/svc/movies/v2/reviews/all.json?order=by-opening-date&api-key=',api_key)
movie_raw <- fromJSON(movie_review_url,flatten=TRUE)

critic_review_url <- str_c('https://api.nytimes.com/svc/movies/v2/critics/all.json?order=by-opening-date&api-key=',api_key)
critic_raw <- fromJSON(critic_review_url,flatten=TRUE)
```

## View Raw Data  
```{r view-movie-review-df}
movie_reviews <- as.data.frame(movie_raw)

kable(head(movie_reviews,2)) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>% scroll_box(width = "125%") 
```
```{r view-critic-review-df}
critic_reviews <- as.data.frame(critic_raw)

kable(head(critic_reviews,2)) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>% scroll_box(width = "125%") 
```


## Cleaner Data  
Let's look at a smaller subset of columns to really get a look at the data  
```{r clean-movie-review-df}
movie_reviews_subset <- select(movie_reviews,results.display_title,results.mpaa_rating,results.byline,results.headline,results.summary_short,results.publication_date,results.link.type,results.link.url)

colnames(movie_reviews_subset) <- c('Display.Title','MPAA.Rating','Byline','Headline','Summary.Short','Publication.Date','Link.Type','Link.URL')

kable(head(movie_reviews_subset,5)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))  %>% scroll_box(width = "125%") 
```

```{r clean-critic-review-df}
critic_reviews_subset <- select(critic_reviews,results.display_name,results.sort_name,results.status,results.bio,results.seo_name)

colnames(critic_reviews_subset) <- c('Display.Name','Sort.Name','Status','Bio','SEO.Name')

kable(head(critic_reviews_subset,5)) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>% scroll_box(width = "125%") 
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
